---
title: "Course Project Part 2"
author: "Ming Wei SIW"
output:
  html_document: 
    keep_md: yes
---

#Overview


#Data Analysis

##Load Data

```{r}
library(datasets)
data("ToothGrowth")
```

##Explore the Data

```{r}
str(ToothGrowth)
#convert dose to a categorical variable
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

Since there is a categorical variable involved, boxplots may be a good exploratory plot.

###Boxplot

```{r}
with(ToothGrowth,
  boxplot(len ~ supp, col = "steelblue", 
          main = "Boxplot of Tooth Length and Supplement Type",
          ylab = "Tooth Length", xlab = "Supplement Type"))
```

The median of tooth length when supplement type is OJ seems to be higher than when supplement type is VC.

###Boxplot of Dose Level and Tooth Length

```{r}
with(ToothGrowth,
     plot(len ~ dose, col = rgb(0.5, 0, 0.5, 0.5), 
          xlab = "Dose Level", ylab = "Tooth Length",
          main = "Boxplot of Dose Level and Tooth Length"))
```

Based on this boxplot, high dose level seems to be linked to greater tooth length.

##Data Summary

```{r}
summary(ToothGrowth)
```

##Summary of Tooth Length by Supplement Type

```{r}
tapply(ToothGrowth$len, ToothGrowth$supp, summary)
```

Supplement type OJ seems to yield greater tooth growth than supplement type VC.

##Summary of Tooth Length by Dose Level

```{r}
tapply(ToothGrowth$len, ToothGrowth$dose, summary)
```

Higher dose level is shown to have greater mean of tooth growth.

##Hypothesis Test

###Mean of Tooth Length by Supplement Type

```{r}
require(statsr)
inference(len, supp, data = ToothGrowth, type = "ht", statistic = "mean",
          method = "theoretical", alternative = "twosided")
```

As p value of hypothesis test is still above 0.05, do not reject null hypothesis that mean values are equal for both supplement type.

###Mean of Tooth Length by Supplement Type (Bootstrap)

```{r}
inference(len, supp, data = ToothGrowth, type = "ht", statistic = "mean",
          method = "simulation", alternative = "twosided")
```

Via bootstrapping with 15000 replications, the p value of hypothesis test is still above 0.05, thus null of equal means between tooth length of different supplement type is not rejected.

###Assumption for Hypothesis Test

- Variables in the dataset must be IID (Independent and Identically Distributed)

- Tooth Growth follows a normal distribution

